Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-11-21 analysis/paper/paper.Rmd
added a citation

The new technology and occupation in high elevation
The new technology appeared around 40-35ka in the Korean Peninsula includes stemmed points and following blade industry. The stemmed points brought new paradigms in stone artifact assemblages. For instance, the concept of composite tool contributed to increase efficiency of maintaining the toolkit by easily replacing the damaged part [@kuhn2015artifacts]. Combining with other materials increases utility or functionality of the tool by adding extra weight and providing a shaft, which makes it earlier to grip. Selective use of raw material might impact on hunter-gathers’ mobility and occupation pattern depending on availability of the specific raw materials such as shale and rhyolite. In addition, this research shows that carrying the points enabled hunter-gatherers to occupy higher elevation compared to the sites with no stemmed points. In other words, the new technology might play an important role to survive in environments with more risks.

>>>>

The new technology and occupation in high elevation
The new technology appeared around 40-35ka in the Korean Peninsula includes stemmed points and following blade industry. The stemmed points brought new paradigms in stone artifact assemblages. For instance,

the concept of composite tool contributed to increase efficiency of maintaining the toolkit by easily replacing the damaged part [@kuhn2015artifacts; @cardillo2010some]. Combining with other materials increases utility or functionality of the tool by adding extra weight and providing a shaft, which makes it earlier to grip. Selective use of raw material might impact on hunter-gathers’ mobility and occupation pattern depending on availability of the specific raw materials such as shale and rhyolite. In addition, this research shows that carrying the points enabled hunter-gatherers to occupy higher elevation compared to the sites with no stemmed points. In other words, the new technology might play an important role to survive in environments with more risks.
